Evolution of a conspicuous dynamic visual signal in an introduced chameleon

### 2021-05-07 ms.Rmd
Need to check contrasts for preddtor models. Something not quite right

  # Check robustness of results to non-indepenedence using Robust Variance Estimator (RVE)
    Predator_IDs <- Predator %>% filter(!is.na(Predator), !is.na(Population)) # filter out misssing data
       robust_PredatorAC <- coef_test(PredatorAC, cluster = Predator_IDs$ID, vcov = "CR2")
    robust_PredatorAC_CI <-  conf_int(PredatorAC, cluster = Predator_IDs$ID, vcov = "CR2")

@@

@@

>>>>

  # Check robustness of results to non-indepenedence using Robust Variance Estimator (RVE)
    Predator_IDs <- Predator %>% filter(!is.na(Predator), !is.na(Population)) # filter out misssing data
       robust_PredatorAC <- coef_test(PredatorAC, cluster = Predator_IDs$ID, vcov = "CR2")
    robust_PredatorAC_CI <-  conf_int(PredatorAC, cluster = Predator_IDs$ID, vcov = "CR2")
     robust_PredatorAC_CI_inter <-  conf_int(PredatorAC_inter, cluster = Predator_IDs$ID, vcov = "CR2")

  # Model allows us to get bird in Hwaii compared to bird in Kenya (contrast 3)
      Predator$pred_pop <- with(Predator, interaction(Predator, Population))

      PredatorAC_pred_pop1 <- lmer(dL ~  pred_pop + (1|ID), data = Predator) 
      summary(PredatorAC_pred_pop1)
      PredatorAC_pred_pop2 <- lmer(dL ~  relevel(pred_pop, ref = "snake.Hawaii") + (1|ID), data = Predator) 
      summary(PredatorAC_pred_pop2)

      # Fit the models so we get the estimate and corrected robust standard error for the contrasts we want to make
      robust_PredatorAC_pred_pop1 <- conf_int(PredatorAC_pred_pop1, cluster = Predator$ID, vcov="CR2")
      robust_PredatorAC_pred_pop2 <- conf_int(PredatorAC_pred_pop2, cluster = Predator$ID, vcov="CR2")

     # Contrasts hypothesis tests, but use RVE 
    result_pred <- Wald_test(PredatorAC_pred_pop, constraints = constrain_pairwise(c(1:4)), vcov="CR2", tidy = TRUE)
    result_pred$p_val_bonfer <- sapply(p.adjust(result_pred$p_val, "bonferroni"), function(x) p_value(x))

    # Get the contrasts and Wald stats for comparions
     CI_hyp_testAC <- data.frame(
              comparison = c("Snake (Hawaii-Kenya)", "Birds (Hawaii-Kenya)"), 
                Estimate = c(robust_PredatorAC_pred_pop2[4,1], robust_PredatorAC_pred_pop1[3, 1]),
                lwr = c(robust_PredatorAC_pred_pop2[4,4], robust_PredatorAC_pred_pop1[3, 4]),
                upr = c(robust_PredatorAC_pred_pop2[4,5], robust_PredatorAC_pred_pop1[3, 5]),
              Fstat = c(result_pred[5,3], result_pred[2,3]),
              df = c(result_pred[5,5], result_pred[2,5]),
              p_val = c(result_pred[5,7], result_pred[2,7]),
              p_bonf = c(result_pred[5,8], result_pred[2,8]))

@@

    # Present full model
         robust_PredatorCC_CI_inter <-  conf_int(PredatorCC, cluster = Predator_IDs$ID, vcov = "CR2")

@@

### Supplementary Tables - Add to Supplement. Easier to generate here given all code is here.

```{r table1, tab.cap = "Model estimates, standard errors (SE), Saitterwaite degrees of freedom (df) and 95% confidence internals (95% CI) comparing acromatic and chromatic mean differences between Kenyan and Hawaiian lizards in two social contexts (Male-Male Competition and Courtship). Standard errors are corrected by using robust variance estimators. "}

table1 <- as.data.frame(rbind(robust_ConspicDisplayAC_CI,
                robust_ConspicDisplayCC_CI,
                robust_ConspicCourtshipAC_CI,
                robust_ConspicCourtshipCC_CI))
table1$Parameter <- rownames(table1)
rownames(table1) <- NULL
# Clean
 final_T1 <- table1 %>% 
             mutate(SocialContext = c("Male-Male Display", rep("", 5), "Courtship Display", rep("", 5)),
                    VisualRealm = c("Acromatic Contrast", rep("", 2), "Chromatic Contrast", rep("", 2), "Acromatic Contrast", rep("", 2), "Chromatic Contrast", rep("", 2))) %>%
              select(SocialContext, VisualRealm, Parameter, beta, SE, df, CI_L, CI_U)

 # Table
table1 <- flextable(final_T1) %>%
        table_style6()

table1
```

```{r table2, tab.cap = ""Model estimates, standard errors (SE), Saitterwaite degrees of freedom (df) and 95% confidence internals (95% CI) comparing acromatic and chromatic mean differences between Kenyan and Hawaiian lizards for snakes and lizards. Full models are provided and standard errors are corrected by using robust variance estimators."}

table2 <- as.data.frame(rbind(robust_PredatorAC_CI_inter,
                              robust_PredatorCC_CI_inter))
table2$Parameter <- rownames(table2)
rownames(table2) <- NULL

# Clean
 final_T2 <- table2 %>% 
             mutate(JND = c("Acromatic Contrast", rep("", 3), "Chromatic Contrast", rep("", 3))) %>%
              select(JND, Parameter, beta, SE, df, CI_L, CI_U)

 # Table
table2 <- flextable(final_T2) %>%
           table_style7()

table2
```

CI_hyp_test
